Statistical Mechanics Informed Neural Networks for Solar Wind modeling

### 2024-11-12 paper/main.tex
paper default

\title{Determining Solar Wind's distribution with Vlasov PINNs}
\author{Jorge D. Enciso}
\date{\today}

@@

\section{Kinetic Models}
In order to fully assume the magnetohydrodynamical model, interactions must converge to the Maxwell-Boltzmann thermodynamical distribution for certain conditions, implying a high colisionality degree, contrary to empirical observations of the Solar Wind. Therefore, the utilization of such a constrictive framework must be carefully evaluated before setting it up as a modeling constraints.

@@

>>>>

\title{Statistical Mechanics Informed Neural Networks for Solar Wind modeling}
\author{Jorge D. Enciso}
\date{\today}

@@

\section{Kinetic models and general constraints}
In order to fully assume the magnetohydrodynamical model, interactions must converge to the Maxwell-Boltzmann thermodynamical distribution for certain conditions, implying a high colisionality degree, contrary to empirical observations of the Solar Wind. Therefore, the utilization of such a constrictive framework must be carefully evaluated before setting it up as a modeling constraints.

@@

\subsection{Liouville's theorem}

\subsection{Entropy}
